---
title: "benap_OriginalHomeworkCode_01"
author: "Ben Peters"
date: "2025-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Challenge Code

```{r}
library(stringr)
```


## Challenge 1

```{r}
barnacle <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed." #input string
barnacle_vector <- str_split(barnacle," ") #convert string barnacle to a vector of individual words
barnacle_vector[[1]][c(3,6,9,12,15,18,21)] #select every 3rd word from barnacle vector
```

> You wrote "str_split()" instead of "strsplit()", which caused an error.


> str_split() is a valid function in stringr, I think you might just not have the package installed

***

## Challenge 2

```{r}
# create matrix m from the hw
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```

extract the 2nd, 3rd, and 6th columns and assign them to the variable x
```{r}
x <- m[ ,c(2,3,6)]
x
```

extract the 6th to 8th row and assign them to the variable x
```{r}
x <- m[c(6:8), ]
x
```

extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x
```{r}
x <- m[c(2:6),c(2:9)]
x
```

***

## Challenge 3

Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)
```{r}
tesseract <- array(400:1, dim = c(5,5,4,4))
```


Given this matrix, what would the following return?
```{r}
tesseract[1, 1, 1, 2]
```
```{r}
tesseract[2, 3, 2, ]
```
```{r}
tesseract[1:5, 1:5, 3, 3]
```

***

## Challenge 4

```{r}
#Strepsirhini
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")

#Haplorhini
Tarsioidea <- c("Tarsiidae")

Catarrhini <- c("Hominidae","Hylobatidae","Cercopithecidae")
Platyrrhini <- c("Pitheciidae","Atelidae","Cebidae")
Anthropoidea <- list(Catarrhini, Platyrrhini)
names(Anthropoidea) <- list("Catarrhini","Platyrrhini")

Haplorhini <- list(Tarsioidea, Anthropoidea)
names(Haplorhini) <- list("Tarsioidea","Anthropoidea")

Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates
```

***

## Challenge 5

Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE.

```{r}
m3_data <- c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2) # I could also define data in the matrix function itself, but for clarity thought I'd do it here instead
m3 <- matrix(data = m3_data, nrow = 5, ncol = 3, byrow = TRUE) # byrow ensures the matrix is filled in row-wise instead of column-wise
m3
```

Coerce the matrix to a data frame.

```{r}
m3_df <- as.data.frame(m3, row.names = c(1,2,3,4,5)) #as.data.frame is a base R function that converts an input (here m3) to a dataframe, row names are specified within the function by the row.names bit
colnames(m3_df) <- c("first","second","third") #rename columns in m3_df so they're not just "V1," "V2," etc.
m3_df
```

> Renaming the rows and columns is a nice touch


> Thanks!

As a data frame, coerce the second column to be logical-valued

```{r}
m3_df$second <- as.logical(m3_df$second) #simple use of the as.logical function, using the $ operator to specify the column we're changing
m3_df
```

As a data frame, coerce the third column to be factor-valued


```{r}
m3_df$third <- as.factor(m3_df$third)
m3_df
```

When you are done, use the str() command to show the data type for each variable in your dataframe.

```{r}
str(m3_df)
```

> Most of what we did is very similar.  I used separate code chunks for different steps of the challenges in order to make my process easier to follow (sort of like in the modules), but that's just personal preference.  That being said, greater annotation may be necessary for more complicated challenges in later weeks.  You don't have any challenges listed, so I assume that--like me--you didn't really encounter any difficulties.  Your variable naming conventions are better than mine; I'll work to integrate that into my code going forward.


> Yeah, noticing the similarities between our work too. Annotation is something I've definitely struggled with in the past, so will try to be better about that going forward too. Re: variable naming conventions, I just get tired of seeing individual letters all the time. Plus I'd be remiss if I missed a chance to reference Nora Barnacle while doing something involving a James Joyce novel. Thanks for the feedback!